---
title: "Lab_3"
format: html
editor: source
---

```{r}
library(tidyverse)
bond.data <- read_csv("data/jamesbond.csv")
bond.data

```

## Which movie earned the most?
```{r}
#code selecting the most profitable bond film from the dataset.
bond.data |>
    select(Year, Movie, US_Gross) |>
    arrange(desc(US_Gross))
```
The most profitable movie was Skyfall, made in 2012. It made a profit of about $300 million.

## Is there a correlation between budget and earnings?
We can check this by creating graphs
```{r}
ggplot(bond.data, aes(x=Budget, y=US_Gross)) +
    geom_point()
# This doesn't account for inflation. Check: add colours for year?
```
This doesn't account for inflation. We can check this by adding colours for the years.

```{r}
ggplot(bond.data, aes(x=Budget, y=US_Gross, color=Year)) +
    geom_point() +
    scale_color_continuous()
```
Definitely looks like year correlates with both earnings and budget. The dataset contains inflation-adjusted numbers, let's use those instead.

## Inflation adjusted numbers
```{r}
ggplot(bond.data, aes(x=Budget_Adj, y=US_Adj, color=Year)) +
    geom_point() +
    scale_color_continuous()
```
Still seems budget is increasing with year even after inflation adjustment, but the correlation with returns is now much less clear.

## Just for fun
Is there a correlation between the number of times Bond says "Bond, James Bond" and return??
```{r}
ggplot(bond.data, aes(x=BJB, y=US_Adj)) +
    geom_point() +
    scale_color_continuous()
```
It seems the movies earn more if he says it 0 or 2 times? Probably a spurious correlation!
